Prey movement shapes the acquisition of predator expertise in a virtual bi-trophic system

### 2024-09-03 manuscript/manuscript.Rmd
MS up to date (corrected ref typo)
minor edit to discussion

Prey speed also mediated differences among predator players in the acquisition of expertise, suggesting that individual predators varied in their capacity to adjust to challenging prey. Animals are expected to have limited attention spans, which restricts diet choice and the formation of search images [@dukars.etal2001]. Hunting faster prey demands specialized cognitive abilities and coordination that are energetically costly [@kelley.magurran2011]. Thus, predators that failed to develop counter-strategies for detecting or chasing faster prey were likely at a disadvantage. Parallel observations have been outlined in studies of prey camouflage strategies. For example, @troscianko.etal2018 showed in a computer experiment involving humans that disruptive camouflage was efficient at preventing the acquisition of expertise during search image formation. Human subjects exposed to a restricted set of strategies were also less efficient compared to those exposed to a variety of strategies. Therefore, our observations show that prey antipredator behaviour can also impair predator expertise acquisition.

Despite adjusting for the prey's speed (i.e. model V), noticeable differences in expertise acquisition among predators persited. One possible explanation is that the predators' hunting tactics may indirectly shape their own expertise through changes in prey behaviour. Predators tend to specialize as cursorial or ambush hunters in *Dead by Daylight* [@fraserfranco.etal2022]. Consequently, those employing a cursorial tactic may push prey to move faster, which, in turn, may hinder their own expertise acquisition due to the increased difficulty of hunting such prey. An alternative explanation is that longer time intervals between hunting events are hypothesized to hinder or delay the acquisition of expertise because individuals may forget information when delays are longer [@endler1991;@wright.etal2022]. For example, a predator that played 300 matches in six months might forget critical information related to prey detection or escape patterns compared to one that played 300 matches in six days. Investigating the impact of such time lags in future analyses may reveal important insights into the outcome of predator-prey interactions. Another potential reason for the persistent differences among individuals is that neither the predator nor prey players' lives are at stake in the game. As a result, emerging patterns may be driven more by the players' motivation to win rather than "true" survival. For example, some players could experiment with the game out of boredom, which could shape how expertise is honed and impede ecologically realistic interpretations of our data.

>>>>

Prey speed also mediated differences among predator players in the acquisition of expertise, suggesting that individual predators varied in their capacity to adjust to challenging prey. Animals are expected to have limited attention spans, which restricts diet choice and the formation of search images [@dukas.etal2001]. Hunting faster prey demands specialized cognitive abilities and coordination that are energetically costly [@kelley.magurran2011]. Thus, predators that failed to develop counter-strategies for detecting or chasing faster prey were likely at a disadvantage. Parallel observations have been outlined in studies of prey camouflage strategies. For example, @troscianko.etal2018 showed in a computer experiment involving humans that disruptive camouflage was efficient at preventing the acquisition of expertise during search image formation. Human subjects exposed to a restricted set of strategies were also less efficient compared to those exposed to a variety of strategies. Therefore, our observations show that prey antipredator behaviour can also impair predator expertise acquisition.

Despite adjusting for the prey's speed (i.e. model V), noticeable differences in expertise acquisition among predators persited. One possible explanation is that the predators' hunting tactics may indirectly shape their own expertise through changes in prey behaviour. Predators tend to specialize as cursorial or ambush hunters in *Dead by Daylight* [@fraserfranco.etal2022]. Consequently, those employing a cursorial tactic may push prey to move faster, which, in turn, may hinder their own expertise acquisition due to the increased difficulty of hunting such prey. An alternative explanation is that longer time intervals between hunting events are hypothesized to hinder or delay the acquisition of expertise because individuals may forget information when delays are longer [@endler1991;@wright.etal2022]. For example, a predator that played 300 matches in six months might forget critical information related to prey detection or escape patterns compared to one that played 300 matches in six days. Investigating the impact of such time lags in future analyses may reveal important insights into the outcome of predator-prey interactions. Another potential reason for the persistent differences among individuals is that neither the predator nor prey players' lives are at stake in the game. As a result, emerging patterns may be driven more by the players' motivation to win rather than "true" survival. For example, some players could experiment with the game out of boredom, which could also contribute in shaping how expertise is honed in this particular system.
